A Switching Planner for Combined Task and Observation Planning

### 2011-02-07 code/subarchitectures/planner.sa/trunk/src/latex/AAAI11/conc.tex
corrections

From an automated planning perspective, the problem of practical
mobile robot control poses important and contrary challenges.
%%
On the one hand, planning and execution monitoring must be
lightweight, robust, timely, and should span the lifetime of the
robot. Those processes must seamlessly accommodate exogenous events,
changing objectives, and the underlying unpredictability of the
environment.
%%
On the other hand, robot planning should perform computationally
expensive reasoning about contingencies, and possible revisions of
subjective belief according to quantitatively modelled uncertainty in
acting and sensing.

In this paper we address these challenges, developing a continual
planner that switches between fast sequential and expensive
decision-theoretic planning. Given a POMDP model of the environment,
sequential planning is used to compute an initial deterministic
sequential plan and complementary runtime evolution of the decision
process. That plan is executed until testing of an assumption about
the runtime state is scheduled. At that point a contingent session
performs some sensing which determines whether or not the sequential
session should be allowed to continue, or otherwise acts to achieve
the overall objectives.

The most pressing item for future research, is to develop a scheme
whereby the serial planner can relax {\em executability} assumptions,
so that conformant (or semi-conformant) plans can be executed without
interruption by a contingent session. A more general criticism of
switching continual planning concerns interleaved sequential and
contingent sessions failing to make any progress towards the
objectives. For example, in the worst case we can have each sequential
session producing an identical plan, and each decision-theoretic
session rejecting it without further sensing. Although this has not
been an issue in our work so far, it must be dealt with rigorously
in the future. We suggest that a good way to mitigate this problem is
by developing a {\em motivational} component that maintains a {\em
dynamic} reward model whose limiting behaviour prevents that switching
deadlock.

>>>>

\vspace{-1ex}

For use in an integrated continual planning and execution monitoring
system on a mobile robot platform, we developed a base planner that
switches between fast sequential and expensive DT planning. Given a
DTPDDL model of the environment, sequential planning is used to
compute an initial deterministic sequential plan and complementary
runtime evolution of the decision process. That plan is executed until
testing of an assumption about the runtime state is scheduled. At that
point a DT session performs some sensing which determines whether or
not the sequential session should be allowed to continue, or otherwise
acts to achieve the overall objectives. We find our approach performs
quickly and relatively efficiently in a number of large real-world
task and observation planning problems.

\Omit{
The most pressing item for future research, is to develop a scheme
whereby the serial planner can relax {\em executability} assumptions,
so that conformant (or semi-conformant) plans can be executed without
interruption by a DT session. A more general criticism of
switching continual planning concerns interleaved sequential and
DT sessions failing to make any progress towards the
objectives. For example, in the worst case we can have each sequential
session producing an identical plan, and each decision-theoretic
session rejecting it without further sensing. Although this has not
been an issue in our work so far, it must be dealt with rigorously
in the future. We suggest that a good way to mitigate this problem is
by developing a {\em motivational} component that maintains a {\em
dynamic} reward model whose limiting behaviour prevents that switching
deadlock.
}
